Historical Soil Organic Carbon Budget

### 2020-03-23 SOCbudgetPaper/methods.Rmd
Update methods.Rmd

### Livestock Distribution and Manure Excretion	(300)
Since their is no native, biophysical indicator to disaggregate country level FAOSTAT livestock production values to half-degree pattern, we use the following rule based assumptions:

* Based on the development state of a country, we devide poultry, egg and monogastric meat production into intensive and extensive systems.

* Extensive production is allocated to urban area share within a country based on the assumption that these animals are held in households, subsistence or small-holder farming systems that are labour rich.

@@

* We split dairy and ruminated meat production into pasture fed and non-pasture fed fractions based on the aggregated feed mix within a country

@@

* Pasture fed animals are apportioned to half-degree cells according to the pasture production shares of that cell within a country.

* Non-pasture fed animals are distributed again using crop production (excluding 2nd generation bioenergy crops) shares.

<!-- Add formular, drawings or visualisation here? -->

@@

We calculate excretions using the nitrogen balance of the livestock system ([@bodirsky1012]) by assuming that every feed intake not incoorpared in the slaugher mass, has to excreted. Using C:N ratios (given by [(@ipcc_2019_2019)]) we estimate carbon content

### Irrigation (100)
Simple growing period calculations together with irrigation shares of LUH2v2 are used (BB: you dont like d's, on't you?) to estimate water effects on decay rates.

>>>>

### Livestock Distribution and Manure Excretion	(300)

To disaggregate country level FAOSTAT livestock production values to half-degree pattern, we use the following rule based assumptions which was inspired by the approach of [@gilbert].

For poultry, egg and monogastric meat production we 
* divide into intensive and extensiv eproduction systems based on a per-capita (explain rules in more detail)

* Based on the development state (thats not a fixed term) of a country, we devide poultry, egg and monogastric meat production into intensive and extensive systems.

* Extensive production is allocated to built-up area share <!-- built-up is the more correct terminology for our urban are --> within a country based on the assumption that these animals are held in households, subsistence or small-holder farming systems.

@@

For dairy and ruminated meat production we

* splot into pasture fed and non-pasture fed fractions based on the aggregated feed mix within a country (explain rules)

@@

* Pasture fed animals are distributed to half-degree cells according to the pasture production shares of that cell within a country (not methodologically clear description).

* Non-pasture fed animals are distributed again using crop production (excluding 2nd generation bioenergy crops) shares (not clear, either).

<!-- Add formular, drawings or visualisation here? --> <!-- No formulas needed, but precise wording -->

@@

We calculate excretions by first estimating the nitrogen balance of the livestock system ([@bodirsky1012]) on the basis of comprehensive livestock feed baskets ([weindl]), assuming that all nitrogen in protein feed intake, minus the nitrogen in the slaugher mass, is excreted. 
Carbon in excreted manure is estimated by applying fixed C:N ratios (given by [(@ipcc_2019_2019)]).
What about animal waste management losses?

### Irrigation (100)
Simple growing period calculations together with irrigation shares of LUH2v2 are used (BB: you dont like d's, on't you) to estimate water effects on decay rates.
